PM Mungbean meta-analysis

### 2019-06-20 02_Weather.Rmd
Moving weather data to it's own chapter

# Preliminary Analysis

```{r PA_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
#source("./getPPD2.R")

## Summary of data

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports

PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

glimpse(PM.dat)

kable(PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   scroll_box(width = "900px", height = "500px")

PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)

## Weather data

@@

experiment_sites <- data.frame(
   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
   lat = c(-28.215 ,-26.58,-27.56,-23.54),
   lon = c(152.1003,151.83,152.32,148.19)
)

 leaflet() %>%
    addProviderTiles("Esri.WorldTopoMap") %>%
    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)
# ______  Kingaroy_______

@@

ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
              aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, color = Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Hermitage")+
   scale_y_continuous(limits = c(0,40))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))

@@

# ______  Gatton  _______
max_T <- vector()
min_T <- vector()
for(i in 1:length(silo_gatton_Tmax[,1])){
   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
}
# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
# Add columns for Year and date to data
Gat_Tm_aver <- Gat_Tm_aver %>%
   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
          Day = year.day(Gat_Tm_aver$date)) 
# Create data subset of Powdery mildew data means for the first sign of the disease by location
Gatton_FS <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
   filter(Location == "Gatton") %>%
   mutate(Year = factor(substr(First_sign,1,4)),
          Day = year.day(First_sign))
ggplot(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year)),
               aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Gatton")+
   scale_y_continuous(limits = c(0,40))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))

# line 259
vec1 <- year.day(Herm_FS$First_sign)
```

### Yield saved from fungicide applications

The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table. All data are a list of mean values from each treatment applied in each experiment. Various factors have been studied in the previous experiments which may influence the following results. The following variables were disregarded in the plots below.

   1) Fungicide type
   2) Fungicide dose
   3) row spacing
   4) Host cultivars
   5) Experiment location
   6) Final disease rating

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
library(lme4)

# Which row spacing leads to the highest yield penalty

# `2017-05-11` # last assessment Fogerty
subset(PM_MB_17, location == "Hermitage")
ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
   geom_point()+
   geom_smooth()+
   scale_y_continuous(limits = c(-5,15))
# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# removed the Year interaction with location
yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# Removing Fungicide as different fungicides were sprayed a different number of times
yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# Removing Fungicide as different fungicides were sprayed a different number of times
yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
                    data = PM_MB_means, na.action = na.omit, REML = T)
ranef(yield_lmer4)
anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit)
summary(yield_lmer)
ranef(yield_lmer)
```

#### Yield saved 
##### Number of fungicide applications
The following density plots show mean yield saved in relation to how many sprays were applied.

```{r warning=FALSE, echo=FALSE}
library(ggplot2)
PM_MB_means <- read.csv("./data/1902 powdery mildew-Mungbean - Collated means.csv")

# Making a table of showing the upper and lower percentiles (95%)
quant_PMy <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   group_by(total_Fungicide) %>%
   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
             upper = quantile(yield_gain, na.rm = T, c(0.975)))
# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
   geom_vline(xintercept = 0, size =1)+
   labs(x = "Grain yeild saved (t/ha)",
   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(data = quant_PMy, aes(xintercept = lower, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   geom_vline(data = quant_PMy, aes(xintercept = upper, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
          fill=guide_legend(title="Number of \nFungicide applications"))+
   scale_x_continuous(limits = c(-0.3,0.8))

names(quant_PMy) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
knitr::kable(quant_PMy)
#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
#            caption = "The 'upper' and 'lower' percentiles for yeild saved (t/Ha) against the number of Fungicide sprays in a season. Data from 2011-2017 mungbean experimental means. Data ignores factors such as fungicide, dose, season or location of experiment")
# Making a table of showing the upper and lower percentiles (95%)
quant_PM <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   group_by(total_Fungicide) %>%
   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
             upper = quantile(prop_YG, na.rm = T, c(0.975)))
# Density plot of proportion of yield saved
ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
   geom_vline(xintercept = 0, size =1)+
   labs(x = "Proportion of grain yeild saved",
   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(data = quant_PM, aes(xintercept = lower, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   geom_vline(data = quant_PM, aes(xintercept = upper, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
          fill=guide_legend(title="Number of \nFungicide applications"))+
   scale_x_continuous(limits = c(-0.3,0.55))
names(quant_PM) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
knitr::kable(quant_PM)   
#knitr::kable(quant_PM, 
#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season. Data from 2011-2017 mungbean experimental means. Data ignores factors such as fungicide, dose, season or location of experiment")
```

\n\n\n\n\n\n\n

#### Timing of Fungicide application
The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.

```{r echo = FALSE, message=FALSE, warning=FALSE}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   filter(Year != 2017) %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
colnames(PM_MB_means)
days_from_fungicid <- function(FSD,F1,F2,F3){
   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
   if(is.na(dF1)){
      return(NA)} else{
   if(between(dF1,lower = -1, upper = 1000)){
      return(dF1)}else{
   if(is.na(dF2)){
      return(dF1)}else{
      if(between(dF2,lower = dF1, upper = -0.1)){
            return(dF2)} else{
               return(dF3)}}
            }}
}
vec1<- vector()
for(i in 1:dim(PM_MB_means1)[1]){
   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
   if(is.na(dF1)){
      vec1 <- c(vec1,dF1)} else{
         if(between(as.numeric(dF1),-1, 1000)){
            vec1 <- c(vec1,dF1)}else{
               if(is.na(dF2)){
                  vec1 <- c(vec1,dF1)}else{
                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
            vec1 <- c(vec1,dF2)} else{
               if(as.numeric(dF3)>=0){
                  vec1 <- c(vec1,dF2)} else{
                     vec1 <- c(vec1,dF3)}}}
            }}
}
PM_MB_means1$spray_diff <- vec1 # gives the 
PM_MB_means1$days_from_1st
#summary(factor(PM_MB_means1$days_from_1st))
# Density plot of proportion of yield saved
ggplot(PM_MB_means1, aes(prop_YG))+
   geom_density(aes(group = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20)), 
                    fill = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))), alpha = 0.3)+
   geom_vline(xintercept = 0, size =1)+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="First spray window\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.55))
###########################################3
unique(PM_MB_means1$days_from_1st)
ggplot(PM_MB_means1, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~., factor(PM_MB_means1$Fungicide))+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
unique(PM_MB_means1$spray_diff)
ggplot(PM_MB_means1, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
# Making a table of showing the upper and lower percentiles (95%)
quant_PM_prop <- PM_MB_means1 %>%
   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))) %>%
   group_by(cut_daysfrom1st) %>%
   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
             upper = quantile(prop_YG, na.rm = T, c(0.975)))
names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
cat("Lower (2.5) and Upper (97.5) quantiles for the proportion of yield gained, when the first fungicide applied relative to when powdery mildew is first seen")
knitr::kable(quant_PM_prop)   
ggplot(PM_MB_means1, aes(yield_gain))+
   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))~.)+
   scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Grain yield (t/Ha) saved",
   title = "Grain yield (t/Ha) saved, grouped by when the\nfirst fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.4,1.2))
# Making a table of showing the upper and lower percentiles (95%)
quant_PM_prop <- PM_MB_means1 %>%
   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-29,-20,-15,-6,-0.5,0.5,2,10,20))) %>%
   group_by(cut_daysfrom1st) %>%
   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
             upper = quantile(yield_gain, na.rm = T, c(0.975)))
names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
print("Yield gain quantiles when the first fungicide applied relative to when powdery mildew is first seen, Lower (2.5) and Upper (97.5) quantiles of yeild ")
knitr::kable(quant_PM_prop)  

@@

```{r}
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Tebeconazole")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
#__________________________________________________________________________________________________________
levels(factor(PM_MB_means$Fungicide))
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Sulphur" |
             Fungicide == "Sulphur (SC)" |
             Fungicide == "Sulphur (Ultra SC)" |
             Fungicide == "Sulphur (WP)")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))
Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
levels(factor(PM_MB_means$Fungicide))
for(Chem in Chemical){
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == Chem)
cat(Chem)
cat(unique(PM_MB_means2$spray_diff))
p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
   scale_x_continuous(limits = c(-0.3,0.6))
print(p1)
Sys.sleep(10)
}
```

>>>>

# Weather data

@@

@@

ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
              aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, color = Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Hermitage")+
   scale_y_continuous(limits = c(0,45))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))

@@

# ______  Gatton  _______
max_T <- vector()
min_T <- vector()
for(i in 1:length(silo_gatton_Tmax[,1])){
   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
}

# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)

# Add columns for Year and date to data
Gat_Tm_aver <- Gat_Tm_aver %>%
   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
          Day = year.day(Gat_Tm_aver$date))

# Create data subset of Powdery mildew data means for the first sign of the disease by location
Gatton_FS <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(Location == "Gatton") %>%
   mutate(Year = factor(substr(First_sign,1,4)),
          Day = year.day(First_sign))

ggplot(subset(Gat_Tm_aver, Year == 2012),
               aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Gatton")+
   scale_y_continuous(limits = c(0,40))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))

@@
